Investigating Neolithic pottery usage in the Yanyuan Basin in Southwest China using organic residue analysis

### 2023-01-14 analysis/paper/paper.Rmd
added a code chunk for maps to the rmd

# Geographical and Cultural Background of Guijiabao in Yanyuan Basin
<!--Info about Yanyuan area-->
The Yanyuan area in Sichuan province is a pull-apart basin located in the middle eastern part of the Hengduan Mountain, which is a group of parallel mountain ranges in a north-south direction from the Tibetan Plateau to Yunnan-Guizhou Plateau. Although the ranges isolate areas with their own unique geographic conditions and cultures, river valleys provide pathways for the movements of people and the exchange of goods between cultural groups since the prehistoric period [@Lin2022; @Hao2022]. Therefore, the archaeological sites in the Yanyuan Basin are important to understanding the cultural interactions between southwest China and other regions, including northwest China, the Sichuan area, and northwest Yunnan.

>>>>

# Geographical and Cultural Background of Guijiabao in Yanyuan Basin

```{r SW-china-map, fig.cap = "The archaeological sites, Guijiabao and Gaoshan, and other locations in Southwest China that are mentioned in this study. Map data is from naturalearthdata.com"}
library(here)
knitr::include_graphics(here("analysis", "figures", "Sichuan-sites-map.png"))
```

<!--Info about Yanyuan area-->
The Yanyuan area in Sichuan province is a pull-apart basin located in the middle eastern part of the Hengduan Mountain, which is a group of parallel mountain ranges in a north-south direction from the Tibetan Plateau to Yunnan-Guizhou Plateau (Figure \@ref(fig:SW-china-map)). Although the ranges isolate areas with their own unique geographic conditions and cultures, river valleys provide pathways for the movements of people and the exchange of goods between cultural groups since the prehistoric period [@Lin2022; @Hao2022]. Therefore, the archaeological sites in the Yanyuan Basin are important to understanding the cultural interactions between southwest China and other regions, including northwest China, the Sichuan area, and northwest Yunnan.
